---
title       : Impact on MPG of Various Features by Transmission Type in mtcars Data
subtitle    : Developing Data Products - Course Project, Sep 2014
author      : 
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Executive Summary


This deck provides an analysis and visualization of fuel consumption (**MPG**) as it is impacted by various features of a car.

Further, the visualization is shown broken down by transmission type (manual or automatic).

The fundamental *assumption* in this analysis is that the observations are independent of the make/brand of the car.

( Data source: **mtcars** )

```{r, echo=FALSE}
data(mtcars)
```

---

## Summary of Analysis

Intuitively, it is obvious that MPG must be impacted by many, if not most features, of a car. The impact can be quantified like this:
```{r, echo=FALSE}
summary( lm(mpg ~ ., data=mtcars ) )  ## interactions by variable
```

---
## Summary of Analysis (*contd.*)

Looking at MPG by weight:

```{r, echo=FALSE}
ggplot(mtcars, aes(x=wt, y=mpg))+geom_point()+geom_smooth(aes(group=as.factor(mtcars$am)),method="lm") +
  ggtitle("MPG by Weight grouped by Transmission Type")
```

---
## Conslusions

* There is a gain in MPG when switching to manual transmission from automatic.
* Somewhat surprisingly, this analysis has shown that the type of transmission does not significantly impact the MPG versus other factors such as weight, gears, cylinders, etc; except in the case of the number of carburetors.



